```{r}
load("./strokeStudy.RData")
```

```{r}
library(ggplot2)
library(dplyr)
library(nlme)
library(broom)
library(knitr)
library(stringr)
library(tidyverse)
library(janitor)
library(naniar)
library(mice)
```

# EDA
```{r}
time_stage_levels <- c("baseline", "mid", "final")

x <- x %>%
  clean_names() %>%
  rename(emsvscar = em_svs_car) %>%
  mutate(
    race2 = na_if(race2, "Missing"),
    race2 = factor(race2),
    site_id = factor(site_id),
    home_num = as.integer(home_or_rehab),
    notify_num = case_when(
      pre_hosp_notify == "Yes" ~ 1,
      pre_hosp_notify == "No" ~ 0,
      TRUE ~ NA_real_
    ),
    transport_num = case_when(
      emsvscar == 1 ~ 1,
      emsvscar == 0 ~ 0,
      TRUE ~ NA_real_
    ),
    gender_num = if_else(gender == "Female", 1, 0),
    time_stage = case_when(
      time2 %in% c("Y1Q1", "Y1Q2") ~ "baseline",
      time2 %in% c("Y1Q3", "Y1Q4", "Y2Q1", "Y2Q2") ~ "mid",
      time2 %in% c("Y2Q3", "Y2Q4") ~ "final",
      TRUE ~ NA_character_
    ),
    time_stage = factor(time_stage, levels = time_stage_levels)
  )

str(x)
```

missingness per variable
```{r}
na_table <- x %>% 
  summarise(across(everything(), ~ sum(is.na(.)))) %>% 
  pivot_longer(everything(),
               names_to = "variable",
               values_to = "n_missing") %>%
  arrange(desc(n_missing))


```

missingness aggregated by site
```{r}
x %>%
  group_by(site_id) %>%
  summarise(across(everything(), ~ mean(is.na(.)))) %>%
  pivot_longer(-site_id, names_to = "variable", values_to = "prop_missing") %>%
  ggplot(aes(x = variable, y = site_id, fill = prop_missing)) +
  geom_tile() +
  scale_fill_viridis_c() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Missingness by Site")
```

```{r}
x %>%
  ggplot(aes(x = home_or_rehab, y = age, fill = home_or_rehab)) +
  geom_boxplot() +
  labs(title = "Age Differences by Outcome")
```

```{r}
x %>% 
  ggplot(aes(x = gender, fill = home_or_rehab)) +
  geom_bar(position = "fill") +
  labs(y = "Proportion", 
       title = "Outcome by Gender")

```

```{r}
x %>% 
  ggplot(aes(x = race2, fill = home_or_rehab)) +
  geom_bar(position = "fill") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Proportion", 
       title = "Outcome by Race")
```

```{r}
x <- x %>%
  mutate(ems_label = case_when(
    emsvscar == 1 ~ "EMS Arrival",
    emsvscar == 0 ~ "Car Arrival",
    TRUE ~ "Missing"
  ))
x %>% 
  ggplot(aes(x = ems_label, fill = home_or_rehab)) +
  geom_bar(position = "dodge") +
  labs(title = "Outcome by Arrival Method",
       x = "Arrival Method",
       y = "Count",
       fill = "Good Outcome") +
  scale_fill_manual(values = c("FALSE" = "tomato", "TRUE" = "steelblue"))
```

missingness by quarter
```{r}
x %>%
  group_by(time2) %>%
  summarise(across(everything(), ~ mean(is.na(.)))) %>%
  pivot_longer(-time2, names_to = "variable", values_to = "prop_missing") %>%
  ggplot(aes(variable, time2, fill = prop_missing)) +
  geom_tile() +
  scale_fill_viridis_c() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Missingness by Quarter")
```

missingness correlation plot
```{r}
vis_miss(x)
```

missingness by time stage
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)

x %>%
  group_by(time_stage) %>%
  summarise(across(everything(), ~ mean(is.na(.))), .groups = "drop") %>%
  pivot_longer(
    cols = -time_stage,
    names_to = "variable",
    values_to = "prop_missing"
  ) %>%
  ggplot(aes(x = variable, y = time_stage, fill = prop_missing)) +
  geom_tile(color = "white") +
  scale_fill_viridis_c(
    name  = "Proportion\nMissing",
    labels = scales::percent_format(accuracy = 1)
  ) +
  labs(
    title = "Missingness by Time Stage (Baseline / Mid / Final)",
    x = "Variable",
    y = "Time Stage"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

```

age missingness by site x quarter

```{r}
x %>%
  mutate(age_missing = is.na(age)) %>%
  group_by(site_id, time2) %>%
  summarise(prop_age_missing = mean(age_missing), .groups = "drop") %>%
  ggplot(aes(x = time2, y = site_id, fill = prop_age_missing)) +
  geom_tile(color = "white") +
  scale_fill_viridis_c(labels = scales::percent_format(accuracy = 1)) +
  labs(
    title = "Share of Records Missing Age by Site and Quarter",
    fill = "Percent\nMissing"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Can clearly see that this is not MCAR; its MAR.

# Missing data + Frequentist model

use predictive mean matching by drawing 20 multiply imputed data sets



```{r}
impute_vars <- x %>%
   dplyr::select(
    home_or_rehab, age, gender, race2, emsvscar, pre_hosp_notify,
    had_tpa, had_thrombectomy, tpa_complic, thr_complic,
    site_id, time2
  )

meth <- make.method(impute_vars)
meth["age"] <- "pmm"

pred <- make.predictorMatrix(impute_vars)
pred["age", ] <- 0
pred["age", c("gender", "race2", "emsvscar", "pre_hosp_notify",
              "had_tpa", "had_thrombectomy", "tpa_complic",
              "thr_complic", "site_id", "time2", "home_or_rehab")] <- 1

set.seed(2025)
imp <- mice(
  impute_vars,
  m = 20,
  maxit = 20,
  method = meth,
  predictorMatrix = pred,
  seed = 2025,
  printFlag = FALSE
)

imp
```
constructs 20 predictive-mean-matching imputations for Age using the specified covariates

```{r}
fit1_mi <- with(
  imp,
  glm(
    home_or_rehab ~ age + gender + race2 + emsvscar + pre_hosp_notify +
      had_tpa + had_thrombectomy + tpa_complic + thr_complic + time2,
    family = binomial
  )
)

pool(fit1_mi) %>% summary(conf.int = TRUE, exponentiate = TRUE)
```
fits the logistic model within each imputed dataset and pools odds ratios that respect imputation uncertainty.
# Frequentist model diagnostics

1. first imputed dataset
```{r}
comp1 <- complete(imp, 1)  # first imputed dataset

fit_fixed <- glm(
  home_or_rehab ~ age + gender + race2 + emsvscar + pre_hosp_notify +
    had_tpa + had_thrombectomy + tpa_complic + thr_complic + time2,
  data = comp1,
  family = binomial
)
comp1$pred <- predict(fit_fixed, type="response")

```

```{r}
library(lme4)

fit_mixed <- glmer(
  home_or_rehab ~ age + gender + race2 + emsvscar + pre_hosp_notify +
    had_tpa + had_thrombectomy + tpa_complic + thr_complic + time2 +
    (1 | site_id),
  data   = comp1,
  family = binomial
)
```
random effect for site id is extremely small (variance close to 0)
```{r}
pearson_res <- residuals(fit_fixed, type = "pearson")

# Overdispersion ratio
overdisp_fixed <- sum(pearson_res^2) / df.residual(fit_fixed)
overdisp_fixed
pearson_res_mixed <- residuals(fit_mixed, type = "pearson")
overdisp_mixed <- sum(pearson_res_mixed^2) / df.residual(fit_mixed)
overdisp_mixed
```
≈ 1 → no overdispersion in both fixed & mixed model
-> adding site effect doesnt reduce dispersion


2. all imputed datasets
```{r}
cal_list <- lapply(1:imp$m, function(k) {
  dat_k <- complete(imp, k)

  fit_k <- glm(
    home_or_rehab ~ age + gender + race2 + emsvscar + pre_hosp_notify +
      had_tpa + had_thrombectomy + tpa_complic + thr_complic + time2,
    data = dat_k,
    family = binomial
  )

  dat_k$pred <- predict(fit_k, type = "response")

  dat_k %>%
    mutate(
      bin = ntile(pred, 10),
      imp = k
    ) %>%
    group_by(imp, bin) %>%
    summarise(
      mean_pred = mean(pred),
      obs_rate  = mean(home_or_rehab),
      .groups   = "drop"
    )
})

cal_all <- bind_rows(cal_list)
```


# calibration plot
```{r}
library(arm)

cal <- comp1 %>%
  mutate(bin = ntile(pred, 10)) %>%
  group_by(bin) %>%
  summarise(
    mean_pred = mean(pred),
    obs_rate = mean(home_or_rehab)
  )

ggplot(cal, aes(mean_pred, obs_rate)) +
  geom_point(size=3) +
  geom_abline(slope=1, intercept=0, linetype="dashed", color="red") +
  labs(title="Calibration Plot",
       x="Mean Predicted Probability",
       y="Observed Proportion")
```
```{r}
ggplot(cal_all, aes(x = mean_pred, y = obs_rate)) +
  geom_point(size = 1.8) +
  geom_abline(slope = 1, intercept = 0,
              linetype = "dashed", color = "red") +
  coord_equal(xlim = c(0,1), ylim = c(0,1)) +
  facet_wrap(~ imp) +
  labs(
    title = "Calibration Plots Across Imputations",
    x = "Mean Predicted Probability",
    y = "Observed Proportion"
  )
```

# ROC curve
```{r}
library(pROC)
roc_obj <- roc(comp1$home_or_rehab, comp1$pred)

auc_value <- auc(roc_obj)


plot(1 - roc_obj$specificities,
     roc_obj$sensitivities,
     type = "l",
     col = "steelblue",
     xlab = "1 – Specificity (False Positive Rate)",
     ylab = "Sensitivity",
     main = "ROC Curve")

abline(0, 1, lty = 2, col = "gray")
text(
  x = 0.6, y = 0.1,
  labels = paste("AUC =", round(auc_value, 3)),
  cex = 1.3
)
```
```{r}
roc_list <- lapply(1:20, function(k) {
  dat_k <- complete(imp, k)

  fit_k <- glm(
    home_or_rehab ~ age + gender + race2 + emsvscar + pre_hosp_notify +
      had_tpa + had_thrombectomy + tpa_complic + thr_complic + time2,
    data = dat_k,
    family = binomial
  )

  pred_k <- predict(fit_k, type = "response")

  roc(dat_k$home_or_rehab, pred_k)
})

# Turn ROC curves into a data frame
roc_df <- lapply(seq_along(roc_list), function(k) {
  data.frame(
    imp = k,
    fpr = 1 - roc_list[[k]]$specificities,  # 1 - specificity
    tpr = roc_list[[k]]$sensitivities       # sensitivity
  )
}) %>% bind_rows()

# AUC per imputation (for optional labels)
auc_values <- sapply(roc_list, auc)
auc_df <- data.frame(
  imp = 1:20,
  auc = auc_values
)

# Faceted ROC plots
ggplot(roc_df, aes(x = fpr, y = tpr)) +
  geom_line(color = "steelblue") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "gray") +
  facet_wrap(~ imp) +
  labs(
    title = "ROC Curves Across Imputations",
    x = "1 – Specificity (False Positive Rate)",
    y = "Sensitivity"
  ) +
  # Optional: add AUC text inside each facet
  geom_text(
    data = auc_df,
    aes(x = 0.7, y = 0.1,
        label = paste0("AUC = ", round(auc, 3))),
    inherit.aes = FALSE,
    size = 3
  )
```



# which variables were predictive of missingness
```{r}
x$miss_age <- ifelse(is.na(x$age), 1, 0)
find_predictors_of_missingness <- function(var) {
  
  # 1. Create missingness indicator
  miss_indicator <- as.numeric(is.na(x[[var]]))
  
  # 2. Build dataset with predictors (drop the variable being tested)
  predictors <- x[, setdiff(names(x), var), drop = FALSE]
  
  # 3. Combine into one dataframe
  data_miss <- data.frame(miss = miss_indicator, predictors)
  
  # 4. Fit logistic regression
  fit <- glm(miss ~ ., data = data_miss, family = binomial)
  
  return(summary(fit))
}

find_predictors_of_missingness("age")


```
indicates perfect separation (complete separation)
missingness mechanism is

Not random. but structural, driven by site and quarter






# Bayesian model

Reference patient
```{r}
age_ref    <- median(x$age, na.rm = TRUE)
gender_ref <- as.numeric(names(sort(table(x$gender_num), decreasing = TRUE))[1])
ems_ref    <- as.numeric(names(sort(table(x$transport_num), decreasing = TRUE))[1])
age_ref
gender_ref
ems_ref

```
age = 70
gender = 0 (female)
race = Caucasian
EMS = 0, notify = 0
TPA = 0, thrombectomy = 0, no complications
site effect = average = 0


```{r}
model_string <- "
model {

  ################################################
  # 0. OUTCOME MODEL: home_or_rehab
  ################################################

  for (i in 1:N) {
    # Binary outcome
    home[i] ~ dbern(p[i])

    # Logistic mixed model
    logit(p[i]) <-
        beta0 +
        beta_age   * age[i] +
        beta_gender * gender[i] +          # 0/1
        beta_ems   * transport[i] +        # EMS vs car
        beta_not   * notify[i] +           # pre-hosp notification
        beta_tpa   * had_tpa[i] +
        beta_thr   * had_thromb[i] +
        beta_tpaC  * tpa_comp[i] +
        beta_thrC  * thr_comp[i] +
        beta_time[ time_stage[i] ] +
        beta_race[race[i]] +               # race coded 1..nRace
        u_site_out[ site[i] ]              # site random effect
  }

  # Priors for outcome fixed effects
  beta0       ~ dnorm(0, 1.0E-4)
  beta_age    ~ dnorm(0, 1.0E-4)
  beta_gender ~ dnorm(0, 1.0E-4)
  beta_ems    ~ dnorm(0, 1.0E-4)
  beta_not    ~ dnorm(0, 1.0E-4)
  beta_tpa    ~ dnorm(0, 1.0E-4)
  beta_thr    ~ dnorm(0, 1.0E-4)
  beta_tpaC   ~ dnorm(0, 1.0E-4)
  beta_thrC   ~ dnorm(0, 1.0E-4)

  # Time (quarter) effects
  beta_time[1] <- 0                     # baseline = reference level

for (t in 2:nTimeStage) {             # mid, final
  beta_time[t] ~ dnorm(0, 1.0E-4)
}

  # Race effects, first category as reference (Caucasian)
  for (r in 2:nRace) {
    beta_race[r] ~ dnorm(0, 1.0E-4)
  }
  beta_race[1] <- 0

  # Site random intercepts for outcome
  for (s in 1:nSite) {
    u_site_out[s] ~ dnorm(0, tau_site_out)
  }
  tau_site_out <- pow(sigma_site_out, -2)
  sigma_site_out ~ dunif(0, 2)


  ################################################
  # 1. AGE MODEL: age | transport, notify, site, time, gender
  #    (p(age | transport, notify, z))
  ################################################

  for (i in 1:N) {
    age[i] ~ dnorm(mu_age[i], tau_age)
    mu_age[i] <-
        alpha0 +
        alpha_time[ time_stage[i] ] +
        alpha_gender * gender[i] +
        alpha_tr     * transport[i] +   # allow EMS to shift age mix
        alpha_not    * notify[i] +      # allow notification to shift age mix
        u_site_age[ site[i] ]           # site random effect
  }

  alpha0       ~ dnorm(0, 1.0E-4)
  alpha_gender ~ dnorm(0, 1.0E-4)
  alpha_tr     ~ dnorm(0, 1.0E-4)      
  alpha_not    ~ dnorm(0, 1.0E-4)     

  for (t in 1:nTimeStage) {
    alpha_time[t] ~ dnorm(0, 1.0E-4)
  }

  for (s in 1:nSite) {
    u_site_age[s] ~ dnorm(0, tau_site_age)
  }

  tau_age        <- pow(sigma_age, -2)
  sigma_age      ~ dunif(0, 50)      # age in years
  tau_site_age   <- pow(sigma_site_age, -2)
  sigma_site_age ~ dunif(0, 20)


  ################################################
  # 2. NOTIFY MODEL: notify | transport, site, time, gender
  #    (p(notify | transport, z))
  ################################################

  for (i in 1:N) {
    # notify is only meaningful if transport == 1 (EMS).
    # If transport[i] = 0, then pi_not[i] ≈ 0, so notify[i] ≈ 0.
    notify[i] ~ dbern(pi_not[i])

    pi_not[i] <- transport[i] * pi_ems[i] + (1 - transport[i]) * 1.0E-6

    logit(pi_ems[i]) <-
        delta0 +
        delta_time[ time_stage[i] ] +
        delta_gender * gender[i] +
        u_site_not[ site[i] ]
  }

  delta0        ~ dnorm(0, 1.0E-4)
  delta_gender  ~ dnorm(0, 1.0E-4)    
  for (t in 1:nTimeStage) {
    delta_time[t] ~ dnorm(0, 1.0E-4)
  }

  for (s in 1:nSite) {
    u_site_not[s] ~ dnorm(0, tau_site_not)
  }
  tau_site_not <- pow(sigma_site_not, -2)
  sigma_site_not ~ dunif(0, 2)


  ################################################
  # 3. TRANSPORT MODEL: transport | site, time, gender
  #    (p(transport | z))
  ################################################

  for (i in 1:N) {
    transport[i] ~ dbern(pi_tr[i])

    logit(pi_tr[i]) <-
        gamma0 +
        gamma_time[ time_stage[i] ] +
        gamma_gender * gender[i] +
        u_site_tr[ site[i] ]
  }

  gamma0        ~ dnorm(0, 1.0E-4)
  gamma_gender  ~ dnorm(0, 1.0E-4)     
  for (t in 1:nTimeStage) {
    gamma_time[t] ~ dnorm(0, 1.0E-4)
  }

  for (s in 1:nSite) {
    u_site_tr[s] ~ dnorm(0, tau_site_tr)
  }
  tau_site_tr <- pow(sigma_site_tr, -2)
  sigma_site_tr ~ dunif(0, 2)


  ################################################
  # 4. RACE MODEL: race | site (LAST in ordering)
  ################################################

  for (i in 1:N) {
    race[i] ~ dcat(pi_race[ site[i], 1:nRace ])
  }

  for (s in 1:nSite) {
    pi_race[s, 1:nRace] ~ ddirch(alpha[])
  }
  
  ################################################
  # 5. DERIVED QUANTITIES: baseline vs final stages
  ################################################
  beta_time_baseline <- beta_time[ baseline_stage ]
  beta_time_final    <- beta_time[ final_stage ]

  # Overall program effect on log-odds and OR
  time_effect <- beta_time_final - beta_time_baseline
  OR_time     <- exp(time_effect)
  
  # Reference patient settings:
  # age_ref = 70, gender = 0, race = reference (nRace),
  # no EMS, no notify, no TPA/thrombectomy/complications,
  # and average site random effect (0).
  age_ref <- 70

  logit_p_baseline <-
      beta0 +
      beta_age * age_ref +
      beta_gender * 0 +
      beta_ems * 0 +
      beta_not * 0 +
      beta_tpa * 0 +
      beta_thr * 0 +
      beta_tpaC * 0 +
      beta_thrC * 0 +
      beta_time_baseline +
      beta_race[nRace] +   # = 0
      0                    # average u_site_out

  logit_p_final <-
      beta0 +
      beta_age * age_ref +
      beta_gender * 0 +
      beta_ems * 0 +
      beta_not * 0 +
      beta_tpa * 0 +
      beta_thr * 0 +
      beta_tpaC * 0 +
      beta_thrC * 0 +
      beta_time_final +
      beta_race[nRace] +
      0

  p_baseline <- exp(logit_p_baseline) / (1 + exp(logit_p_baseline))
  p_final    <- exp(logit_p_final)    / (1 + exp(logit_p_final))
  improvement <- p_final - p_baseline

}
"

```

```{r}
baseline_stage <- which(levels(x$time_stage) == "baseline")
final_stage    <- which(levels(x$time_stage) == "final")

data_list <- list(
  N      = nrow(x),
  nSite  = nlevels(x$site_id),
  nTimeStage = nlevels(x$time_stage),
  nRace  = nlevels(x$race2),

  home      = x$home_num,                          # 0/1
  age       = x$age,                               # numeric, NA allowed
  notify    = x$notify_num,                        # 0/1, NA allowed
  transport = x$transport_num,                     # 0/1, NA allowed
  had_tpa   = as.integer(x$had_tpa),
  had_thromb= as.integer(x$had_thrombectomy),
  tpa_comp  = as.integer(x$tpa_complic),
  thr_comp  = as.integer(x$thr_complic),

  gender = x$gender_num,                           # 0/1
  race   = as.integer(x$race2),                    # 1..nRace, NA allowed

  site   = as.integer(x$site_id),                  # 1..nSite
  time_stage = as.integer(x$time_stage),           # 1..nTimeStage

  alpha  = rep(0.5, nlevels(x$race2)),              # Jeffreys prior for race
  baseline_stage = baseline_stage,
  final_stage    = final_stage
)
```

```{r}
library(rjags)

results_dir <- "results"
samples_path <- file.path(results_dir, "posterior_samples_jags.rds")
summary_path <- file.path(results_dir, "posterior_summary.rds")
stats_path   <- file.path(results_dir, "posterior_statistics.csv")

if (!dir.exists(results_dir)) {
  dir.create(results_dir, recursive = TRUE)
}

if (file.exists(samples_path) && file.exists(summary_path)) {
  posterior_samples <- readRDS(samples_path)
  posterior_summary <- readRDS(summary_path)
} else {
  jmod <- jags.model(
    textConnection(model_string),
    data = data_list,
    n.chains = 3
  )

  update(jmod, 2000)

  params_of_interest <- c(
    "beta0", "beta_age", "beta_gender", "beta_ems", "beta_not",
    "beta_tpa", "beta_thr", "beta_tpaC", "beta_thrC",
    "beta_time", "beta_race",
    "sigma_site_out", "sigma_age", "sigma_site_age",
    "sigma_site_not", "sigma_site_tr"
  )

  posterior_samples <- coda.samples(
    jmod,
    variable.names = params_of_interest,
    n.iter = 8000
  )

  posterior_summary <- summary(posterior_samples)

  saveRDS(posterior_samples, samples_path)
  saveRDS(posterior_summary, summary_path)
  write.csv(
    posterior_summary$statistics,
    stats_path,
    row.names = TRUE
  )
}

posterior_summary
```
# Trace plots
```{r}
old_par <- par(no.readonly = TRUE)
par(mfrow = c(2, 2), mar = c(3, 3, 2, 1))
plot(posterior_samples[, c("beta0", "beta_age", "beta_tpa", "beta_thr")])
par(old_par)
```
Need to look into the mixing for beta0 and beta_age. 

# Gelman-Rubin Diagnostic
```{r}
gelman_diag <- gelman.diag(posterior_samples, multivariate = FALSE)
gelman_diag
```
Most potential scale-reduction factors are near 1, so indicates that the three chains mixed well.

# Effective Size Results
```{r}
ess_values <- effectiveSize(posterior_samples)
ess_values
```

# Posterior Results
```{r}
posterior_stats <- posterior_summary$statistics %>%
  as.data.frame() %>%
  tibble::rownames_to_column("parameter")

posterior_quants <- posterior_summary$quantiles %>%
  as.data.frame() %>%
  tibble::rownames_to_column("parameter")

posterior_table <- posterior_stats %>%
  dplyr::select(parameter, Mean, SD) %>%
  left_join(
    posterior_quants %>%
      dplyr::select(parameter, `2.5%`, `50%`, `97.5%`),
    by = "parameter"
  ) %>%
  filter(
    stringr::str_detect(
      parameter,
      "^(beta_(age|tpa|thr|ems|not|time|race)|sigma_site_out)"
    )
  )

posterior_table %>%
  arrange(parameter) %>%
  knitr::kable(digits = 3, caption = "Posterior means and 95% credible intervals.")
```

```{r}
posterior_table %>%
  filter(stringr::str_detect(parameter, "^beta")) %>%
  mutate(
    OR_mean = exp(Mean),
    OR_low  = exp(`2.5%`),
    OR_high = exp(`97.5%`)
  ) %>%
  dplyr::select(parameter, OR_mean, OR_low, OR_high) %>%
  arrange(parameter) %>%
  knitr::kable(digits = 3, caption = "Posterior odds ratios for key covariates.")
```

# Residual Plots
